Refinements for open pNets

### 2021-07-21 2021-Refinement/paper/refinementarticle.tex
part of example

As an example, the traffic light system  that controls  
 traffic at the intersection of a busy highway. In Figure \ref{fig:tls} we model it as open automaton and abstract the timer   as  Holes: a controller and a counter.

\begin{figure}
\centering
\input{Traffic_Lights_Spec.tex}
\caption{The specification of a traffic light system}
\label{fig:tls}
\end{figure}

\begin{figure}
%\centering
\input{Traffic_Lights_Controller.tex}
\input{Traffic_Lights_Register.tex}
\caption{On the left: An example of controller agent; On the right: An example of counter agent}
\label{fig:tlh}
\end{figure}

This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
It is supposed to be a single traffic light.

\begin{figure}
\centering
\input{Traffic_Lights_Full.tex}
\caption{The full traffic lights system}
\label{fig:tlf}
\end{figure}

>>>>

As an example, the traffic light system  that controls  
 traffic at the intersection of a busy highway. The open automaton  
modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
is on (Red, Yellow or Green). It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer. The color switches when the counter and the controller component agree that the time is over. The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.

The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer. On the left, the controller component designed to be connected in the hole $\symb{ctl}$.  Its role is to decide the duration before switching the lights. 
We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third. On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$. It measures elapsed model time in ticks by counting ticks until the time limit retrieved beforehand is reached, then emits an over action with the elapsed time and restart.

In Figure \ref{fig:tlf} we present the composition of the three automata. Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.

\begin{figure}
\centering
\input{Traffic_Lights_Spec.tex}
\caption{The specification of a Traffic Light system}
\label{fig:tls}
\end{figure}

\begin{figure}
%\centering
\input{Traffic_Lights_Controller.tex}
\input{Traffic_Lights_Register.tex}
\caption{(a) An example of controller component ~~  (b) An example of counter component}
\label{fig:ctlandcnt}
\end{figure}

\begin{figure}
\centering
\input{Traffic_Lights_Full.tex}
\caption{The full Traffic Lights system}
\label{fig:tlf}
\end{figure}
